EDA

### 2024-12-03 other/EDA/EDA.qmd
added monthly spend graph

View(df)

@@

>>>>

#View(df)

@@

df <- df %>%
  mutate(Month = month(award_date, label = TRUE, abbr = FALSE))

# Aggregate total amount awarded per month
monthly_trends <- df %>%
  group_by(Month) %>%
  summarize(Total_Amount = sum(amount, na.rm = TRUE)) %>%
  ungroup()

# Order the months correctly
monthly_trends$Month <- factor(monthly_trends$Month, levels = month.name)

# Plot the bar chart
ggplot(monthly_trends, aes(x = Month, y = Total_Amount / 1e9)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(
    title = "Total Amount Awarded by Month",
    x = "Month",
    y = "Total Amount Awarded (Billions)"
  ) +
  theme_minimal() +
  scale_y_continuous(labels = comma)

```{r fig-template101}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center
